---
title: "R Notebook"
output: html_notebook
---

This notebook compares results between Formatted Annual Data and Formatted Annual Data v2. The former was done by J. Stewart, whereas the latter was done by me. Results should be the same but a few inconsistencies were found recently (Apr 2023). So, I'm comparing each one to see where the problem is.

```{r}
rm(list = ls())
library(tidyverse)
library(lubridate)
library(flextable)
library(readr)

source("Piedras_Blancas_fcns.R")

```


```{r}
dir.1 <- "data/Formatted Annual Data/"
dir.2 <- "data/Formatted Annual Data v2/"
data.dir <- "data/All data/"

files.1 <- list.files(path = dir.1, 
                    pattern = "Formatted.csv")

col.def.1 <- cols(Week = col_integer(),
                  Date = col_date(format = "%d-%b-%y"),
                  Effort = col_double(),
                  Sightings = col_integer())

col.def.1.2 <- cols(Week = col_integer(),
                  Date = col_date(format = "%d-%b-%Y"),
                  Effort = col_double(),
                  Sightings = col_integer())

col.def.1.3 <- cols(Week = col_integer(),
                    Date = col_date(format = "%Y-%m-%d"),
                    Effort = col_double(),
                    Sightings = col_integer())

col.def.1.1997 <- cols(Week = col_integer(),
                       Date = col_character(), #date(format = "%d-%b-%y"),
                       Effort = col_double(),
                       Sightings = col_integer())

files.2 <- list.files(path = dir.2, 
                    pattern = "Formatted_inshore_v2.csv")

col.def.2 <- cols(Week = col_integer(),
                  Date = col_date(format = "%Y-%m-%d"),
                  Shift = col_integer(),
                  Effort = col_double(),
                  Sightings = col_integer())

fcn.compare.data <- function(data.1, data.2, year){
  data.1 %>% 
    group_by(Date) %>%
    summarize(daily.effort.1 = sum(Effort),
              daily.sightings.1 = sum(Sightings)) %>%
    mutate(Date.char = as.character(Date)) %>%
    dplyr::select(-Date) -> daily.summary.1 
  
  data.2 %>% 
    group_by(Date) %>%
    summarize(daily.effort.2 = sum(Effort),
              daily.sightings.2 = sum(Sightings)) %>%
    mutate(Date.char = as.character(Date)) %>%
    dplyr::select(-Date) -> daily.summary.2 
  
  daily.summary.1 %>% 
    left_join(daily.summary.2, by = "Date.char") %>%
    mutate(dif.effort = daily.effort.1 - daily.effort.2,
           dif.sightings = daily.sightings.1 - daily.sightings.2) -> daily.summary.1.2

  daily.summary.1.2 %>% 
    filter(!is.na(dif.effort)) %>%
    filter(!is.na(dif.sightings)) -> daily.summary.1.2
  
  p.1 <- ggplot(daily.summary.1.2) +
    geom_point(aes(x = as.Date(Date.char), y = dif.effort)) +
    xlab("Date") + 
    ylab("Differences in effort") +
    ggtitle(year)
    
  p.2 <- ggplot(daily.summary.1.2) +
    geom_point(aes(x = as.Date(Date.char), y = dif.sightings),
               color = "red") +
    xlab("Date") + 
    ylab("Differences in # sightings") +
    ggtitle(year)
  
  p. <- cowplot::plot_grid(p.1, p.2)
  
  out.list <- list(data.1 = data.1,
                   data.2 = data.2,
                   daily.summary.1 = daily.summary.1,
                   daily.summary.2 = daily.summary.2,
                   daily.summary.1.2 = daily.summary.1.2,
                   figure = p.,
                   year = year)
  return(out.list)  
}

```


```{r}
years <- c(1994:2019, 2021, 2022)
col.defs.1 <- list(col.def.1, col.def.1.1997, col.def.1.2, col.def.1.3)
col.defs.1.idx <- c(rep(1, 3), rep(2, 23), 3, 4)

daily.summary.list <- list()
k <- 1

for (k in 1:length(years)){
  
  Y <- years[k]
  
  if (col.defs.1.idx[k] == 2){
    data.1 <- read_csv(file = paste0(dir.1, Y, " Formatted.csv"),
                       col_types = col.defs.1[[col.defs.1.idx[k]]]) %>%
      mutate(Date.1 = as.Date(paste0(Date, "-", Y), format = "%d-%b-%Y")) %>%
      transmute(Week = Week, 
                Date = Date.1, 
                Effort = Effort, 
                Sightings = Sightings)
  } else if (col.defs.1.idx[k] == 4){
    data.1 <- read_csv(file = paste0(dir.1, Y, " Formatted.csv"),
                       col_types = col.defs.1[[col.defs.1.idx[k]]]) 
    
  } else {
    data.1 <- read_csv(file = paste0(dir.1, Y, " Formatted.csv"),
                       col_types = col.defs.1[[col.defs.1.idx[k]]]) 
    
  }
  
  data.2 <- read_csv(file = paste0(dir.2, Y, " Formatted_inshore_v2.csv"),
                     col_types = col.def.2)
  
  daily.summary.list[[k]]  <- fcn.compare.data(data.1, data.2, Y)
  
}


```


1994 

```{r}
Y <- 1994
daily.summary.list[[which(years == Y)]]$figure 
```


```{r}
# Code chunk from Extract Excel data.Rmd
dir.name <- paste0("C_C ", Y)
start.time <- "630"

xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[1])
xls.file.name.offshore <- paste0(data.dir, dir.name, "/", xls.files[2])

# lists in the following lines are stored in Piedras_Blancas_fcns.R

idx.list <- which(names(list.sheet.names.inshore) == paste0("Y", Y))
out.list <- get.all.data(list.sheet.names.inshore[[idx.list]], 
                         list.sheet.names.offshore[[idx.list]],
                         list.col.types.inshore[[idx.list]], 
                         list.col.types.offshore[[idx.list]],
                         list.col.names.inshore[[idx.list]], 
                         list.col.names.offshore[[idx.list]],
                         Year = Y, 
                         xls.file.name.inshore, xls.file.name.offshore,
                         start.time)

```


Effort:
```{r}

effort.dif.list <- find.effort.dif(Y, daily.summary.list, out.list)

```

There were `r length(effort.dif.list$date.dif)` differences between the two extraction algorithms for year `r Y`. Many differences come from the first shift starting at 0630, rather than 0700. In the v1 extraction algorithm, the first shift was assumed to start at 0700, so 30 min were removed, whereas the v2 algorithm counts all data. Spot checks show v2 doing a good job counting all. v1 seems to ignore sea state > 4. 

There are a few shift 5... I think they should be deleted. They have been removed. 2023-05-12

Here are the differences.

1. `r effort.dif.list$date.dif[1]`

Data:
```{r}
effort.dif.list$raw.data[[1]]
```


Version 1 extraction:
```{r}
effort.dif.list$dif.1[[1]]

```


Version 2 extraction:
```{r}
effort.dif.list$dif.2[[1]]

```

Observation started at 0630 (Event = 1). So, I think it makes sense to include extra 30 minutes.


2. `r effort.dif.list$date.dif[2]`

There were `r length(effort.dif.list$raw.data[[2]]` differences between V1 and V2 extractions within `r effort.dif.list$date.dif[2]`.

(1) 

Data:
```{r}
effort.dif.list$raw.data[[2]][[1]]
```

The first shift started at 0631 and ended at 1000. However, the visibility became 5 at 0950. So, the effort for this shift should be 3 hr and 19 min (or 199 minutes or 3.3167 hrs).


(2) 

```{r}
effort.dif.list$raw.data[[2]][[2]]
```

This shift started at 1000, paused at 1230 (2.5 hrs), restarted at 1252, then ended at 1300 (8 minutes or 0.133 hrs). So the total effort was 2.633 hrs.


(3)

```{r}
effort.dif.list$raw.data[[2]][[3]]
```

There was no effort for this shift because the sea state was at 5 the entire time.

Version 1 extraction:
```{r}
effort.dif.list$dif.1[[2]]

```


Version 2 extraction:
```{r}
effort.dif.list$dif.2[[2]]

```

V1 did not include 0631 - 0700 for Shift 1. 

I don't know how V1 computed 1.8 hrs for Shift 2. 

High sea state was not considered for Shift 3. It's unclear how 1 hr of effort for this shift was computed


3. `r effort.dif.list$date.dif[3]`

Data:
```{r}
effort.dif.list$raw.data[[3]]
```

Because of the high sea state during Shift 4 (Beaufort 5 and 6), no effort should have been calculated. 

Version 1 extraction:
```{r}
effort.dif.list$dif.1[[3]]

```


Version 2 extraction:
```{r}
effort.dif.list$dif.2[[3]]

```

V1 computed 0.62 hrs of effort for Shift 4. This should have been zero. 


4. `r effort.dif.list$date.dif[4]`

Data:
```{r}
effort.dif.list$raw.data[[4]]
```

Sea state changed from 4 to 5 at 0922 so the effort was from 0630 to 0922 (2 hrs and 52 min or 2.867 hrs). 

Version 1 extraction:
```{r}
effort.dif.list$dif.1[[4]]

```


Version 2 extraction:
```{r}
effort.dif.list$dif.2[[4]]

```

V1 correctly excluded Beaufort 5 but did not include 0630 to 0700. 


```{r}

sightings.dif.list <- find.sightings.dif(Y, daily.summary.list, out.list)

```

For the number of sightings, there were `r length(sightings.dif.list$date.dif` differences. Checking each one of them with raw data, v2 seems to be doing the right counts. 


5. `r effort.dif.list$date.dif[5]`

Data:
```{r}
effort.dif.list$raw.data[[5]]
```



Version 1 extraction:
```{r}
effort.dif.list$dif.1[[5]]

```


Version 2 extraction:
```{r}
effort.dif.list$dif.2[[5]]

```

V1 did not include 0630 - 0700.

6. `r effort.dif.list$date.dif[6]`

Data:
```{r}
effort.dif.list$raw.data[[6]]
```

Version 1 extraction:
```{r}
effort.dif.list$dif.1[[6]]

```


Version 2 extraction:
```{r}
effort.dif.list$dif.2[[6]]

```

The difference comes from whether or not to include 0629 - 0700 as search effort.


7. `r effort.dif.list$date.dif[7]`

Data:
```{r}
effort.dif.list$raw.data[[7]]
```

Version 1 extraction:
```{r}
effort.dif.list$dif.1[[7]]

```


Version 2 extraction:
```{r}
effort.dif.list$dif.2[[7]]

```

The difference comes from whether or not to include 0630 - 0700 as search effort.



8. `r effort.dif.list$date.dif[8]`

Data:
```{r}
effort.dif.list$raw.data[[8]]
```

Version 1 extraction:
```{r}
effort.dif.list$dif.1[[8]]

```


Version 2 extraction:
```{r}
effort.dif.list$dif.2[[8]]

```

The difference comes from whether or not to include 0630 - 0700 as search effort.



9. `r effort.dif.list$date.dif[9]`

Data:
```{r}
effort.dif.list$raw.data[[9]]
```

Version 1 extraction:
```{r}
effort.dif.list$dif.1[[9]]

```


Version 2 extraction:
```{r}
effort.dif.list$dif.2[[9]]

```

The difference comes from whether or not to include 0630 - 0700 as search effort.



10. `r effort.dif.list$date.dif[10]`

There were `r length(effort.dif.list$raw.data[[10]]` differences for `r effort.dif.list$date.dif[10]`.

Data:

(1)

```{r}
effort.dif.list$raw.data[[10]][[1]]
```


(2)

```{r}
effort.dif.list$raw.data[[10]][[2]]
```
The first shift was ended at 0957. The next effort started at 1450. So, there was no Shift 2 on 1994-03-30. 


(3)

```{r}
effort.dif.list$raw.data[[10]][[3]]
```



Version 1 extraction:
```{r}
effort.dif.list$dif.1[[10]]

```


Version 2 extraction:
```{r}
effort.dif.list$dif.2[[10]]

```

For Shift 1, V1 did not include 0628 - 0700.

For Shift 2, V1 somehow gave a full effort (3 hrs) but the data show 0 hrs of effort.

For Shift 3, the effort started at 1450, rather than 1300. So, the true effort was 1450 - 1600 (70 min or 1.167 hrs)




11. `r effort.dif.list$date.dif[11]`

Data:
```{r}
effort.dif.list$raw.data[[11]]
```

Version 1 extraction:
```{r}
effort.dif.list$dif.1[[11]]

```


Version 2 extraction:
```{r}
effort.dif.list$dif.2[[11]]

```

Sea state was 5 from 1600 to 1700. Effort was from 1700 to 1800 (1 hr). 


12. `r effort.dif.list$date.dif[12]`

Data:
```{r}
effort.dif.list$raw.data[[12]]
```

Version 1 extraction:
```{r}
effort.dif.list$dif.1[[12]]

```


Version 2 extraction:
```{r}
effort.dif.list$dif.2[[12]]

```

V1 did not consider 0630 - 0700.



Sightings:

```{r}

sightings.dif.list <- find.sightings.dif(Y, daily.summary.list, out.list)

```

There were `r length(sightings.dif.list$date.dif)` differences between V1 and V2 extractions.


1. `r sightings.dif.list$date.dif[1]`

Data:
```{r}
sightings.dif.list$raw.data[[1]] 
```

Version 1 extraction:
```{r}
sightings.dif.list$dif.1[[1]]

```


Version 2 extraction:
```{r}
sightings.dif.list$dif.2[[1]]

```

During the third shift, there were 7 sightings, of which 2 were sighted at very end of the shift. Is it possible that they were counted in the next shift in V1 extraction? Did V2 double count these? It's likely that they are double counted. Look at the counting code for errors. 

```{r}
out.list$data.inshore %>% filter(Date == "1994-04-20", Shift == 3)
```



1995 

```{r}
Y <- 1995
daily.summary.list[[which(years == Y)]]$figure 
```

Some differences found... 

Get the raw data
```{r}

```


Effort:
```{r}

effort.dif.list <- find.effort.dif(Y, daily.summary.list, out.list)

```


Sightings

```{r}

sightings.dif.list <- find.sightings.dif(Y, daily.summary.list, out.list)

```



1996 

```{r}
daily.summary.list[[which(years == 1996)]]$figure 
```


1997 

```{r}
daily.summary.list[[which(years == 1997)]]$figure 
```

1998 

```{r}
daily.summary.list[[which(years == 1998)]]$figure
```

1999 

```{r}
daily.summary.list[[which(years == 1999)]]$figure
```


2000 

```{r}
daily.summary.list[[which(years == 2000)]]$figure
```


2001 

```{r}
daily.summary.list[[which(years == 2001)]]$figure
```




2002

```{r}
daily.summary.list[[which(years == 2002)]]$figure
```


2003

```{r}
daily.summary.list[[which(years == 2003)]]$figure
```

2004

```{r}
daily.summary.list[[which(years == 2004)]]$figure
```

2005

```{r}
daily.summary.list[[which(years == 2005)]]$figure
```


2006

```{r}
daily.summary.list[[which(years == 2006)]]$figure
```


2007

```{r}
Y <- 2007
daily.summary.list[[which(years == Y)]]$figure
```

2008

```{r}
Y <- 2008

daily.summary.list[[which(years == Y)]]$figure
```


2009

```{r}
Y <- 2009

daily.summary.list[[which(years == Y)]]$figure
```


2010

```{r}
Y <- 2010

daily.summary.list[[which(years == Y)]]$figure
```


2011

```{r}
Y <- 2011

daily.summary.list[[which(years == Y)]]$figure

```


2012

```{r}
Y <- 2012

daily.summary.list[[which(years == Y)]]$figure
```


2013

```{r}
Y <- 2013

daily.summary.list[[which(years == Y)]]$figure
```


2014

```{r}
Y <- 2014

daily.summary.list[[which(years == Y)]]$figure
```


2014

```{r}
Y <- 2014

daily.summary.list[[which(years == Y)]]$figure
```


2015

```{r}
Y <- 2015

daily.summary.list[[which(years == Y)]]$figure
```


2016

```{r}
Y <- 2016

daily.summary.list[[which(years == Y)]]$figure
```


2017

```{r}
Y <- 2017

daily.summary.list[[which(years == Y)]]$figure
```


2018

```{r}
Y <- 2018

daily.summary.list[[which(years == Y)]]$figure
```

2019

```{r}
Y <- 2019

daily.summary.list[[which(years == Y)]]$figure
```


2021

```{r}
Y <- 2021

daily.summary.list[[which(years == Y)]]$figure
```

There are a few discrepancies... 



2022

```{r}
Y <- 2022

daily.summary.list[[which(years == Y)]]$figure
```

In the previous run, ther was no difference in effort. One extra sighting on 2022-03-31 for V1 (4 sightings) compared with V2 (3 sightings). Raw data file (PiedrasBlancas2022SurveyData_postQC_TE.xlsx) contains only three sightings on 2022-03-31. So V2 is correct.

Today... 2023-04-28, there are a lot more differences. Not sure what happened here. I was using old files. Using files that were extracted on 2023-04-19, there was only one difference. Those new files were uploaded to Google folder.



