---
title: "R Notebook"
output: html_notebook
---

This notebook compares results between Formatted Annual Data and Formatted Annual Data v2. The former was done by J. Stewart, whereas the latter was done by me. Results should be the same but a few inconsistencies were found recently (Apr 2023). So, I'm comparing each one to see where the problem is.

```{r}
library(tidyverse)
library(lubridate)
library(flextable)
library(readr)
```


```{r}
dir.1 <- "data/Formatted Annual Data/"
dir.2 <- "data/Formatted Annual Data v2/"

files.1 <- list.files(path = dir.1, 
                    pattern = "Formatted.csv")

col.def.1 <- cols(Week = col_integer(),
                  Date = col_date(format = "%d-%b-%y"),
                  Effort = col_double(),
                  Sightings = col_integer())

col.def.1.2 <- cols(Week = col_integer(),
                  Date = col_date(format = "%d-%b-%Y"),
                  Effort = col_double(),
                  Sightings = col_integer())

files.2 <- list.files(path = dir.2, 
                    pattern = "Formatted.csv")

col.def.2 <- cols(Week = col_integer(),
                  Date = col_date(format = "%Y-%m-%d"),
                  Shift = col_integer(),
                  Effort = col_double(),
                  Sightings = col_integer())

fcn.compare.data <- function(data.1, data.2){
  data.1 %>% 
    group_by(Date) %>%
    summarize(daily.effort.1 = sum(Effort),
              daily.sightings.1 = sum(Sightings)) %>%
    mutate(Date.char = as.character(Date)) %>%
    dplyr::select(-Date) -> daily.summary.1 
  
  data.2 %>% 
    group_by(Date) %>%
    summarize(daily.effort.2 = sum(Effort),
              daily.sightings.2 = sum(Sightings)) %>%
    mutate(Date.char = as.character(Date)) %>%
    dplyr::select(-Date) -> daily.summary.2 
  
  daily.summary.1 %>% 
    left_join(daily.summary.2, by = "Date.char") %>%
    mutate(dif.effort = daily.effort.1 - daily.effort.2,
           dif.sightings = daily.sightings.1 - daily.sightings.2) -> daily.summary.1.2

  p. <- ggplot(daily.summary.1.2) +
    geom_point(aes(x = as.Date(Date.char), y = dif.effort)) +
    geom_point(aes(x = as.Date(Date.char), y = dif.sightings),
               color = "red") +
    xlab("Date") + 
    ylab("Differences in effort (black) and # sightings (red)")
  
  out.list <- list(daily.summary.1 = daily.summary.1,
                   daily.summary.2 = daily.summary.2,
                   daily.summary.1.2 = daily.summary.1.2,
                   figure = p.)
  return(out.list)  
}

```

1994 

```{r}
Y <- 1994
data.1 <- read_csv(file = paste0(dir.1, Y, " Formatted.csv"),
                        col_types = col.def.1) 

data.1 %>% 
  mutate(Shift = rep(1:8, times = nrow(data.1)/8)) -> tmp


data.2 <- read_csv(file = paste0(dir.2, Y, " Formatted.csv"),
                        col_types = col.def.2)

daily.summary.1994 <- fcn.compare.data(data.1, data.2)

daily.summary.1994$figure 
```

There are a lot of differences between the two. Need to look into this a bit more. 

2021

```{r}
Y <- 2021

# The date format is different from earlier days. So, I use the same column definitions as V2

data.1 <- read_csv(file = paste0(dir.1, Y, " Formatted.csv"),
                   col_types = col.def.1.2) 

data.2 <- read_csv(file = paste0(dir.2, Y, " Formatted.csv"),
                   col_types = col.def.2)

daily.summary.2021 <- fcn.compare.data(data.1, data.2)

daily.summary.2021$figure
```

There are a few discrepancies... 



2022

```{r}
Y <- 2022

# The date format is different from earlier days. So, I use the same column definitions as V2

data.1 <- read_csv(file = paste0(dir.1, Y, " Formatted.csv"),
                   col_types = col.def.2) 

data.2 <- read_csv(file = paste0(dir.2, Y, " Formatted.csv"),
                   col_types = col.def.2)

daily.summary.2022 <- fcn.compare.data(data.1, data.2)

daily.summary.2022$figure
```

In the previous run, ther was no difference in effort. One extra sighting on 2022-03-31 for V1 (4 sightings) compared with V2 (3 sightings). Raw data file (PiedrasBlancas2022SurveyData_postQC_TE.xlsx) contains only three sightings on 2022-03-31. So V2 is correct.

Today... 2023-04-28, there are a lot more differences. Not sure what happened here. 
