---
title: "R Notebook"
output: html_notebook
---

This notebook is used to extract data from original data files in the Excel format. Because the file format changes over time, each year is done separately. 

```{r setup}
rm(list=ls())
library(tidyverse)
library(lubridate)
library(readxl)
source("Piedras_Blancas_fcns.R")

data.dir <- "data/All data/"
#out.dir <- "data/Processed data/"    # completed in May 2022 but needs revisions
out.dir <- "data/Processed data v2/"  # for revising outputs
out.formatted.dir <- "data/Formatted Annual Data v2/"

extract.all.vars <- function(x) {
  x %>%
    mutate(Date = Date.date) %>%
    select(-c(Date.date, Date.char)) %>%
    relocate(Date)
}

extract.shift.vars <- function(x) {
  x %>%
  select(Date.char, Shift, Effort, Mother_Calf, Sea_State, Vis) %>%
  transmute(Date = Date.char,
            Shift = Shift,
            Sea_State = Sea_State,
            Vis = Vis,
            Effort = Effort, 
            Mother_Calf = Mother_Calf) -> x.out
  return(x.out)
}
```


THIS FILE NEEDS TO BE UPDATED AND ANNOTATED BETTER. EACH YEAR HAS A DIFFERENT FORMAT SO ALL THE DIFFERENCES NEED TO BE DESCRIBED IN DETAILS. COMMON FUNCTIONS MAY NOT WORK SO WELL. CURRENTLY IT DOES NOT RUN. 2022-07-27

## 1994

```{r}
Year <- 1994
dir.name <- paste0("C_C ", Year)
#start.time <- "630"
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[1])
xls.file.name.offshore <- paste0(data.dir, dir.name, "/", xls.files[2])

sheet.name.inshore <- "INSHORE LOG"
sheet.name.offshore <- NULL
col.types.inshore <- c("date", "numeric", "text", "numeric", "numeric",
                       "numeric", "numeric", "text", "text")

col.names.inshore <- c("Date", "Event", "Time", "Obs. Code", "Sea State",
                       "Vis. IN", "Cow  / Calf")

col.types.offshore <- c("date", "numeric", "text", "numeric", "numeric",
                        "numeric", "numeric", "numeric", "text", "text")

col.names.offshore <- c("Date", "Event", "Time", "Obs.", "Sea State",
                        "Vis. Code", "Cow/Calf", "Ad./Juv.")

# data.all <- get.all.data(sheet.name.inshore, sheet.name.offshore,
#                           col.types.inshore, col.types.offshore,
#                           col.names.inshore, col.names.offshore,
#                           Year, xls.file.name.inshore, xls.file.name.offshore,
#                           start.time, max.shift = 4) %>% 
#   extract.all.vars()

data.inshore <- get.data(Year = Year, 
                         xls.file.name = xls.file.name.inshore, 
                         sheet.name = sheet.name.inshore,
                         col.types = col.types.inshore, 
                         col.names = col.names.inshore, 
                         start.time = start.time,
                         max.shift = 4) %>%
  mutate(Area = "in")

data.offshore <- get.data(Year = Year,
                          xls.file.name = xls.file.name.offshore,
                          sheet.name = sheet.name.offshore,
                          col.types = col.types.offshore,
                          col.names = all_of(col.names.offshore),
                          start.time = start.time, 
                          max.shift = 4) %>%
  mutate(Area = "off")

data.offshore %>% 
  filter(Mother_Calf > 0) %>%
  rbind(data.inshore) %>%
  arrange(Date.date, Minutes_since_0000) %>% 
  extract.all.vars() -> data.all


# There are some characters, e.g., ?, in columns that don't expect them. 
# Warnings return - Line 665

out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")

out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir, 
                                  Year, " Formatted.csv")

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = 7, 
                          end.hr = 19, 
                          max.shift = 4) %>% extract.shift.vars()

formatted.all.data <- format.output(data.shift, max.shift = 4)

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all)

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift)

if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")

```


## 1995

```{r}
Year <- 1995
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[1])
xls.file.name.offshore <- paste0(data.dir, dir.name, "/", xls.files[2])

sheet.name.inshore <- "Inshore Data"
sheet.name.offshore <- "Offshore Data"
col.types.inshore <- c("date", "numeric", "text", "numeric", "numeric", 
                       "numeric", "numeric", "numeric", "text", "text", 
                       "text", "text", "text", "text", "text", "text")

col.names.inshore <- c("Date",	"Event Code",	"Time",	"Observer Code",	
                       "Sea State",	"Vis In",	"C/C Pairs")

col.types.offshore <- c("date", "numeric", "text", "numeric", 
                        "numeric", "numeric", "numeric", "numeric", 
                        "numeric", "numeric", "numeric", "text")


col.names.offshore <- c("Date",	"Event",	"Time",	"OBS.",
                        "Sea",	"Vis.",	"Cow/Calf")

# data.all <- get.all.data(sheet.name.inshore, sheet.name.offshore,
#                           col.types.inshore, col.types.offshore,
#                           col.names.inshore, col.names.offshore,
#                           Year, xls.file.name.inshore, xls.file.name.offshore,
#                           start.time, max.shift = 4)%>% 
#   extract.all.vars()
# There are some characters, e.g., SN, step for observers, in columns that don't expect them. 
# Warnings return - quite a few. 

data.inshore <- get.data(Year = Year, 
                         xls.file.name = xls.file.name.inshore, 
                         sheet.name = sheet.name.inshore,
                         col.types = col.types.inshore, 
                         col.names = col.names.inshore, 
                         start.time = start.time,
                         max.shift = 4) %>%
  mutate(Area = "in")
  
data.offshore <- get.data(Year = Year,
                          xls.file.name = xls.file.name.offshore,
                          sheet.name = sheet.name.offshore,
                          col.types = col.types.offshore,
                          col.names = all_of(col.names.offshore),
                          start.time = start.time, 
                          max.shift = 4)

data.offshore %>% 
  filter(Mother_Calf > 0) %>%
  rbind(data.inshore) %>%
  arrange(Date.date, Minutes_since_0000) %>% 
  extract.all.vars() -> data.all


out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")

out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = 7, 
                          end.hr = 19, 
                          max.shift = 4) %>% extract.shift.vars()

formatted.all.data <- format.output(data.shift, max.shift = 4)

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all)

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift)

if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")



```



## 1996

Some dates were wrong in the inshore file. They need to be fixed. 

```{r}
Year <- 1996
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[1])
xls.file.name.offshore <- paste0(data.dir, dir.name, "/", xls.files[2])

sheet.name.inshore <- "data"
sheet.name.offshore <- "Sheet1"
col.names.inshore <- c("DATE",	"EVENT CODE",	"TIME", "OBS.",	
                       "SEA STATE",	"VIS (IN/OUT)",	"C/C")

col.types.inshore <- c("date", "numeric", "text", "numeric", 
                       "numeric", "text", "numeric", "numeric", 
                       "numeric", "text", "text", "text", 
                       "text", "text")

col.names.offshore <- c("DATE",	"EVENT CODE",	"TIME", 	"OBS",
                        "VIS",	"SEA ST.",	"C/C")

col.types.offshore <- c("date", "numeric", "text", "numeric", 
                        "numeric", "numeric", "numeric", "numeric", 
                        "numeric", "text",  "text")

# data.all <- get.all.data(sheet.name.inshore, sheet.name.offshore,
#                           col.types.inshore, col.types.offshore,
#                           col.names.inshore, col.names.offshore,
#                           Year, xls.file.name.inshore, xls.file.name.offshore,
#                           start.time, max.shift = 4)%>% 
#   extract.all.vars()
# There are some characters, e.g., SN, step for observers, in columns that don't expect them. 
# Warnings return - quite a few. 

data.inshore <- get.data(Year = Year, 
                         xls.file.name = xls.file.name.inshore, 
                         sheet.name = sheet.name.inshore,
                         col.types = col.types.inshore, 
                         col.names = col.names.inshore, 
                         start.time = start.time,
                         max.shift = 4)  %>%
  mutate(Area = "in")
  


data.offshore <- get.data(Year = Year,
                          xls.file.name = xls.file.name.offshore,
                          sheet.name = sheet.name.offshore,
                          col.types = col.types.offshore,
                          col.names = all_of(col.names.offshore),
                          start.time = start.time, 
                          max.shift = 4)

data.offshore %>% 
  filter(Mother_Calf > 0) %>%
  rbind(data.inshore) %>%
  arrange(Date.date, Minutes_since_0000) %>% 
  extract.all.vars() -> data.all


out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")

out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = 7, 
                          end.hr = 19, 
                          max.shift = 4) %>% extract.shift.vars()

formatted.all.data <- format.output(data.shift, max.shift = 4)

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all)

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift)

if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")


```



## 1997

```{r}
Year <- 1997
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[1])
xls.file.name.offshore <- paste0(data.dir, dir.name, "/", xls.files[2])

sheet.name.inshore <- "LOGS"
sheet.name.offshore <- "LOGS"

col.names.inshore <- c("DATE",	"EVENT",	"TIME",	"OBSER" ,	
                       "VIS I/O",	"SEA STATE", "C/C")

col.types.inshore <- c("date", "numeric", "text", "numeric", 
                       "numeric", "numeric", "text", "text", 
                       "text", "text", "text", "text", 
                       "text", "text")

col.names.offshore <- c("DATE",	"EVENT CODE",	"TIME", "OBS",
                        "VIS", "S STATE",	"COW/CA")

col.types.offshore <- c("date", "numeric", "text", "numeric", 
                        "numeric", "text", "text", "numeric", 
                        "text", "text",  "numeric", "text")

# data.all <- get.all.data(sheet.name.inshore, sheet.name.offshore,
#                           col.types.inshore, col.types.offshore,
#                           col.names.inshore, col.names.offshore,
#                           Year, xls.file.name.inshore, xls.file.name.offshore,
#                           start.time, max.shift = 4)%>% 
#   extract.all.vars()

data.inshore <- get.data(Year = Year, 
                         xls.file.name = xls.file.name.inshore, 
                         sheet.name = sheet.name.inshore,
                         col.types = col.types.inshore, 
                         col.names = col.names.inshore, 
                         start.time = start.time,
                         max.shift = 4)  %>%
  mutate(Area = "in")
  


data.offshore <- get.data(Year = Year,
                          xls.file.name = xls.file.name.offshore,
                          sheet.name = sheet.name.offshore,
                          col.types = col.types.offshore,
                          col.names = all_of(col.names.offshore),
                          start.time = start.time, 
                          max.shift = 4)

data.offshore %>% 
  filter(Mother_Calf > 0) %>%
  rbind(data.inshore) %>%
  arrange(Date.date, Minutes_since_0000) %>% 
  extract.all.vars() -> data.all


out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")

out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = 6.5, 
                          end.hr = 19, 
                          max.shift = 4) %>% extract.shift.vars()

# Warnings with "no non-missing arguments" return when no Vis or SeaState are available in a data chunk
# They turn into NAs

formatted.all.data <- format.output(data.shift, max.shift = 4)

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all)

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift)

if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")


```



## 1998

```{r}
Year <- 1998
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[1])
xls.file.name.offshore <- paste0(data.dir, dir.name, "/", xls.files[2])

sheet.name.inshore <- "LOG"
sheet.name.offshore <- "LOGS"

col.names.inshore <- c("Date",	"Event Code",	"Time",	"Obs",
                       "Vis (I/O)", "Sea State",	"c/c"	)

col.types.inshore <- c("date", "numeric", "text", "numeric", 
                       "numeric", "text", "numeric", "numeric", 
                       "numeric", "text", "text", "text", 
                       "text", "text")

col.names.offshore <- c("Date",	"Event Code",	"Time",	"Obs",	
                        "Vis",	"SeaState",	"c/c")

col.types.offshore <- c("date", "numeric", "text", "numeric", 
                        "numeric", "text", "numeric", "numeric", 
                        "text", "text",  "text", "text")


# data.all <- get.all.data(sheet.name.inshore, sheet.name.offshore,
#                           col.types.inshore, col.types.offshore,
#                           col.names.inshore, col.names.offshore,
#                           Year, xls.file.name.inshore, xls.file.name.offshore,
#                           start.time, max.shift = 4)%>% 
#   extract.all.vars()

data.inshore <- get.data(Year = Year, 
                         xls.file.name = xls.file.name.inshore, 
                         sheet.name = sheet.name.inshore,
                         col.types = col.types.inshore, 
                         col.names = col.names.inshore, 
                         start.time = start.time,
                         max.shift = 4)  %>%
  mutate(Area = "in")
  
data.offshore <- get.data(Year = Year,
                          xls.file.name = xls.file.name.offshore,
                          sheet.name = sheet.name.offshore,
                          col.types = col.types.offshore,
                          col.names = all_of(col.names.offshore),
                          start.time = start.time, 
                          max.shift = 4)

data.offshore %>% 
  filter(Mother_Calf > 0) %>%
  rbind(data.inshore) %>%
  arrange(Date.date, Minutes_since_0000) %>% 
  extract.all.vars() -> data.all


out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")

out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = 6.5, 
                          end.hr = 19, 
                          max.shift = 4) %>% extract.shift.vars()

# same as 1997. Vis and SeaState are probably not filled in. 

formatted.all.data <- format.output(data.shift, max.shift = 4)

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all)

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift)

if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")

```




## 1999

```{r}
Year <- 1999
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[1])
xls.file.name.offshore <- paste0(data.dir, dir.name, "/", xls.files[2])

sheet.name.inshore <- "DATA"
sheet.name.offshore <- "DATA"

col.names.inshore <- c("Date",	"Event Code",	"Time", 	"Obs. Code",
                       "Vis", "Sea State", "C/C")

col.types.inshore <- c("date", "numeric", "text", "numeric", 
                       "numeric", "text", "numeric", "numeric", 
                       "numeric", "text", "text", "text",
                       "text", "text", "text")

# data.out <- read_excel(xls.file.name.inshore,
#                          sheet = sheet.name.inshore,
#                          col_types = col.types.inshore)
#                        
# data.inshore <- get.data(Year = Year,
#                            dir.name = dir.name,
#                            xls.file.name = xls.file.name.inshore,
#                            sheet.name = sheet.name.inshore,
#                            col.types = col.types.inshore,
#                            col.names = col.names.inshore,
#                            area.name = "inshore",
#                            start.time = start.time)

col.names.offshore <- c("Date",	"Event Code",	"Time",	"Observer",	
                        "Vis. Code",	"Sea State",	"C/C")

col.types.offshore <- c("date", "numeric", "text", "numeric", 
                        "numeric", "text", "numeric", "numeric", 
                        "text", "text",  "text", "text")

# 
# data.all <- get.all.data(sheet.name.inshore, sheet.name.offshore,
#                           col.types.inshore, col.types.offshore,
#                           col.names.inshore, col.names.offshore,
#                           Year, xls.file.name.inshore, xls.file.name.offshore,
#                           start.time, max.shift = 4)%>% 
#   extract.all.vars()

data.inshore <- get.data(Year = Year, 
                         xls.file.name = xls.file.name.inshore, 
                         sheet.name = sheet.name.inshore,
                         col.types = col.types.inshore, 
                         col.names = col.names.inshore, 
                         start.time = start.time,
                         max.shift = 4)  %>%
  mutate(Area = "in")
  
data.offshore <- get.data(Year = Year,
                          xls.file.name = xls.file.name.offshore,
                          sheet.name = sheet.name.offshore,
                          col.types = col.types.offshore,
                          col.names = all_of(col.names.offshore),
                          start.time = start.time, 
                          max.shift = 4)

data.offshore %>% 
  filter(Mother_Calf > 0) %>%
  rbind(data.inshore) %>%
  arrange(Date.date, Minutes_since_0000) %>% 
  extract.all.vars() -> data.all


out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")

out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = 7, 
                          end.hr = 19, 
                          max.shift = 4)%>% extract.shift.vars()

# same as before. Vis and SeaState are probably not filled in. 

formatted.all.data <- format.output(data.shift, max.shift = 4)

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all)

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift)

if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")
```



## 2000

```{r}
Year <- 2000
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[1])
xls.file.name.offshore <- paste0(data.dir, dir.name, "/", xls.files[2])

sheet.name.inshore <- "DATA"
sheet.name.offshore <- "LOGS"

col.names.inshore <- c("DATE",	"EVENT",	"TIME",	"OBS.",	
                       "VIS (IN/OUT)",	"SEA STATE",	"C/C")

col.types.inshore <- c("date", "numeric", "text", "numeric", 
                       "numeric", "text", "numeric", "numeric", 
                       "text", "text", "text", "text",
                       "text", "text")

# data.out <- read_excel(xls.file.name.inshore,
#                          sheet = sheet.name.inshore,
#                          col_types = col.types.inshore)
#                        
# data.inshore <- get.data(Year = Year,
#                            dir.name = dir.name,
#                            xls.file.name = xls.file.name.inshore,
#                            sheet.name = sheet.name.inshore,
#                            col.types = col.types.inshore,
#                            col.names = col.names.inshore,
#                            area.name = "inshore",
#                            start.time = start.time)

col.names.offshore <- c("DATE",	"EVENT",	"TIME",	"OBS.",
                        "VIS CODE",	"SEA STATE",	"C/C")

col.types.offshore <- c("date", "numeric", "text", "numeric", 
                        "numeric", "text", "numeric", "numeric", 
                        "text", "text",  "text")


# data.all <- get.all.data(sheet.name.inshore, sheet.name.offshore,
#                           col.types.inshore, col.types.offshore,
#                           col.names.inshore, col.names.offshore,
#                           Year, xls.file.name.inshore, xls.file.name.offshore,
#                           start.time, max.shift = 4)%>% 
#   extract.all.vars()

data.inshore <- get.data(Year = Year, 
                         xls.file.name = xls.file.name.inshore, 
                         sheet.name = sheet.name.inshore,
                         col.types = col.types.inshore, 
                         col.names = col.names.inshore, 
                         start.time = start.time,
                         max.shift = 4)  %>%
  mutate(Area = "in")
  
data.offshore <- get.data(Year = Year,
                          xls.file.name = xls.file.name.offshore,
                          sheet.name = sheet.name.offshore,
                          col.types = col.types.offshore,
                          col.names = all_of(col.names.offshore),
                          start.time = start.time, 
                          max.shift = 4)

data.offshore %>% 
  filter(Mother_Calf > 0) %>%
  rbind(data.inshore) %>%
  arrange(Date.date, Minutes_since_0000) %>% 
  extract.all.vars() -> data.all


out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")

out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = 7, 
                          end.hr = 19, 
                          max.shift = 4)%>% extract.shift.vars()

# same as before. Vis and SeaState are probably not filled in. 

formatted.all.data <- format.output(data.shift, max.shift = 4)

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all)

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift)

if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")

```



## 2001

```{r}
Year <- 2001
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[1])
xls.file.name.offshore <- paste0(data.dir, dir.name, "/", xls.files[2])

sheet.name.inshore <- "LOGS"
sheet.name.offshore <- "LOGS"

col.names.inshore <- c("DATE",	"EVENT",	"TIME",	"OBS.",
                       "VIS I/O",	"SEA ST",	"C/C"	)

col.types.inshore <- c("date", "numeric", "text", "numeric", 
                       "numeric", "text", "numeric", "numeric", 
                       "text", "text", "text", "text",
                       "text", "text")

# data.out <- read_excel(xls.file.name.inshore,
#                          sheet = sheet.name.inshore,
#                          col_types = col.types.inshore)
#                        
# data.inshore <- get.data(Year = Year,
#                            dir.name = dir.name,
#                            xls.file.name = xls.file.name.inshore,
#                            sheet.name = sheet.name.inshore,
#                            col.types = col.types.inshore,
#                            col.names = col.names.inshore,
#                            area.name = "inshore",
#                            start.time = start.time)

col.names.offshore <- c("DATE",	"EVENT",	"TIME",	"OBS",
                        "VIS",	"SEA STATE",	"C/C")

col.types.offshore <- c("date", "numeric", "text", "numeric", 
                        "numeric", "text", "numeric", "numeric", 
                        "text", "text",  "text", "text")


# data.all <- get.all.data(sheet.name.inshore, sheet.name.offshore,
#                           col.types.inshore, col.types.offshore,
#                           col.names.inshore, col.names.offshore,
#                           Year, xls.file.name.inshore, xls.file.name.offshore,
#                           start.time, max.shift = 4)%>% 
#   extract.all.vars()

data.inshore <- get.data(Year = Year, 
                         xls.file.name = xls.file.name.inshore, 
                         sheet.name = sheet.name.inshore,
                         col.types = col.types.inshore, 
                         col.names = col.names.inshore, 
                         start.time = start.time,
                         max.shift = 4) %>%
  mutate(Area = "in")
  
data.offshore <- get.data(Year = Year,
                          xls.file.name = xls.file.name.offshore,
                          sheet.name = sheet.name.offshore,
                          col.types = col.types.offshore,
                          col.names = all_of(col.names.offshore),
                          start.time = start.time, 
                          max.shift = 4)

data.offshore %>% 
  filter(Mother_Calf > 0) %>%
  rbind(data.inshore) %>%
  arrange(Date.date, Minutes_since_0000) %>% 
  extract.all.vars() -> data.all


out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")

out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = 7, 
                          end.hr = 19, 
                          max.shift = 4)%>% extract.shift.vars()

# same as before. Vis and SeaState are probably not filled in. 

formatted.all.data <- format.output(data.shift, max.shift = 4)

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all)

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift)

if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")

```



## 2002

```{r}
Year <- 2002
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[1])
xls.file.name.offshore <- paste0(data.dir, dir.name, "/", xls.files[2])

sheet.name.inshore <- "LOGS"
sheet.name.offshore <- "LOG"

col.names.inshore <- c("DATE",	"EVENT",	"TIME", 	"OBS",
                       "VIS (I/O)",	"SS",	"C/C")

col.types.inshore <- c("date", "numeric", "text", "numeric", 
                       "numeric", "text", "numeric", "numeric", 
                       "text", "text", "text", "text",
                       "text", "text")

# data.inshore <- get.data(Year = Year,
#                            dir.name = dir.name,
#                            xls.file.name = xls.file.name.inshore,
#                            sheet.name = sheet.name.inshore,
#                            col.types = col.types.inshore,
#                            col.names = col.names.inshore,
#                            area.name = "inshore",
#                            start.time = start.time)

col.names.offshore <- c("DATE",	"EVENT",	"TIME",	"OBS",
                        "VIS",	"SS",	"C/C")

col.types.offshore <- c("date", "numeric", "text", "numeric", 
                        "numeric", "text", "numeric", "numeric", 
                        "text", "text",  "text", "text")

# 
# data.all <- get.all.data(sheet.name.inshore, sheet.name.offshore,
#                           col.types.inshore, col.types.offshore,
#                           col.names.inshore, col.names.offshore,
#                           Year, xls.file.name.inshore, xls.file.name.offshore,
#                           start.time, max.shift = 4)%>% 
#   extract.all.vars()

data.inshore <- get.data(Year = Year, 
                         xls.file.name = xls.file.name.inshore, 
                         sheet.name = sheet.name.inshore,
                         col.types = col.types.inshore, 
                         col.names = col.names.inshore, 
                         start.time = start.time,
                         max.shift = 4) %>%
  mutate(Area = "in")
  
data.offshore <- get.data(Year = Year,
                          xls.file.name = xls.file.name.offshore,
                          sheet.name = sheet.name.offshore,
                          col.types = col.types.offshore,
                          col.names = all_of(col.names.offshore),
                          start.time = start.time, 
                          max.shift = 4)

data.offshore %>% 
  filter(Mother_Calf > 0) %>%
  rbind(data.inshore) %>%
  arrange(Date.date, Minutes_since_0000) %>% 
  extract.all.vars() -> data.all


out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")

out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = 7, 
                          end.hr = 19, 
                          max.shift = 4)%>% extract.shift.vars()

formatted.all.data <- format.output(data.shift, max.shift = 4)

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all)

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift)

if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")

```



## 2003

```{r}
Year <- 2003
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[1])
xls.file.name.offshore <- paste0(data.dir, dir.name, "/", xls.files[2])

sheet.name.inshore <- "Logs"
sheet.name.offshore <- "logs"

col.names.inshore <- c("DATE",	"EVENT",	"TIME", 	"OBS",
                       "VIS (I/O)",	"SS",	"C/C")

col.types.inshore <- c("date", "numeric", "text", "numeric", 
                       "numeric", "text", "numeric", "numeric", 
                       "text", "text", "text", "text",
                       "text", "text")

# data.inshore <- get.data(Year = Year,
#                            dir.name = dir.name,
#                            xls.file.name = xls.file.name.inshore,
#                            sheet.name = sheet.name.inshore,
#                            col.types = col.types.inshore,
#                            col.names = col.names.inshore,
#                            area.name = "inshore",
#                            start.time = start.time)

col.names.offshore <- c("DATE",	"EVENT",	"TIME",	"OBS",
                        "VIS",	"SS",	"C/C")

col.types.offshore <- c("date", "numeric", "text", "numeric", 
                        "numeric", "text", "numeric", "numeric", 
                        "text", "text",  "text", "text")

# 
# data.all <- get.all.data(sheet.name.inshore, sheet.name.offshore,
#                           col.types.inshore, col.types.offshore,
#                           col.names.inshore, col.names.offshore,
#                           Year, xls.file.name.inshore, xls.file.name.offshore,
#                           start.time, max.shift = 4)%>% 
#   extract.all.vars()

data.inshore <- get.data(Year = Year, 
                         xls.file.name = xls.file.name.inshore, 
                         sheet.name = sheet.name.inshore,
                         col.types = col.types.inshore, 
                         col.names = col.names.inshore, 
                         start.time = start.time,
                         max.shift = 4) %>%
  mutate(Area = "in")
  
data.offshore <- get.data(Year = Year,
                          xls.file.name = xls.file.name.offshore,
                          sheet.name = sheet.name.offshore,
                          col.types = col.types.offshore,
                          col.names = all_of(col.names.offshore),
                          start.time = start.time, 
                          max.shift = 4)

data.offshore %>% 
  filter(Mother_Calf > 0) %>%
  rbind(data.inshore) %>%
  arrange(Date.date, Minutes_since_0000) %>% 
  extract.all.vars() -> data.all


out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")

out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = 7, 
                          end.hr = 19, 
                          max.shift = 4)%>% extract.shift.vars()

# same as before. Vis and SeaState are probably not filled in. 

formatted.all.data <- format.output(data.shift, max.shift = 4)

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all)

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift)

if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")


```



## 2004

```{r}
Year <- 2004
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[2])
xls.file.name.offshore <- paste0(data.dir, dir.name, "/", xls.files[3])

sheet.name.inshore <- "DATA"
sheet.name.offshore <- "DATA"

col.names.inshore <- c("DATE",	"EVENT",	"TIME", 	"OBS",
                       "VIS (I/O)",	"SS",	"C/C")

col.types.inshore <- c("date", "numeric", "text", "numeric", 
                       "numeric", "text", "numeric", "numeric", 
                       "text", "text", "text", "text",
                       "text", "text")

# data.inshore <- get.data(Year = Year,
#                            dir.name = dir.name,
#                            xls.file.name = xls.file.name.inshore,
#                            sheet.name = sheet.name.inshore,
#                            col.types = col.types.inshore,
#                            col.names = col.names.inshore,
#                            area.name = "inshore",
#                            start.time = start.time)

col.names.offshore <- c("DATE",	"EVENT",	"TIME",	"OBS",	
                        "VIS",	"SS",	"C/C")

col.types.offshore <- c("date", "numeric", "text", "numeric", 
                        "numeric", "text", "numeric", "numeric", 
                        "text", "text",  "text", "text")

# 
# data.all <- get.all.data(sheet.name.inshore, sheet.name.offshore,
#                           col.types.inshore, col.types.offshore,
#                           col.names.inshore, col.names.offshore,
#                           Year, xls.file.name.inshore, xls.file.name.offshore,
#                           start.time, max.shift = 4)%>% 
#   extract.all.vars()

data.inshore <- get.data(Year = Year, 
                         xls.file.name = xls.file.name.inshore, 
                         sheet.name = sheet.name.inshore,
                         col.types = col.types.inshore, 
                         col.names = col.names.inshore, 
                         start.time = start.time,
                         max.shift = 4) %>%
  mutate(Area = "in")
  

data.offshore <- get.data(Year = Year,
                          xls.file.name = xls.file.name.offshore,
                          sheet.name = sheet.name.offshore,
                          col.types = col.types.offshore,
                          col.names = all_of(col.names.offshore),
                          start.time = start.time, 
                          max.shift = 4)

data.offshore %>% 
  filter(Mother_Calf > 0) %>%
  rbind(data.inshore) %>%
  arrange(Date.date, Minutes_since_0000) %>% 
  extract.all.vars() -> data.all



out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")

out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = 7, 
                          end.hr = 19, 
                          max.shift = 4)%>% extract.shift.vars()

# same as before. Vis and SeaState are probably not filled in. 

formatted.all.data <- format.output(data.shift, max.shift = 4)

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all)

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift)

if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")

```



## 2005

```{r}
Year <- 2005
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[1])
xls.file.name.offshore <- paste0(data.dir, dir.name, "/", xls.files[2])

sheet.name.inshore <- "LOGS"
sheet.name.offshore <- "LOGS"

col.names.inshore <- c("DATE",	"EVENT",	"TIME", 	"OBS",
                       "VIS (I/O)",	"SS",	"C/C")

col.types.inshore <- c("date", "numeric", "text", "numeric", 
                       "numeric", "text", "numeric", "numeric", 
                       "text", "text", "text", "text", 
                       "text", "text")

# data.out <- read_excel(xls.file.name.inshore,
#                          sheet = sheet.name.inshore,
#                          col_types = col.types.inshore)

# data.inshore <- get.data(Year = Year,
#                          dir.name = dir.name,
#                          xls.file.name = xls.file.name.inshore,
#                          sheet.name = sheet.name.inshore,
#                          col.types = col.types.inshore,
#                          col.names = col.names.inshore,
#                          area.name = "inshore",
#                          start.time = start.time)

col.names.offshore <- c("DATE",	"EVENT",	"TIME",	"OBS",	
                        "VIS",	"SS",	"C/C")

col.types.offshore <- c("date", "numeric", "text", "numeric", 
                        "numeric", "text", "numeric", "numeric", 
                        "text", "text",  "text", "text")

# 
# data.all <- get.all.data(sheet.name.inshore, sheet.name.offshore,
#                           col.types.inshore, col.types.offshore,
#                           col.names.inshore, col.names.offshore,
#                           Year, xls.file.name.inshore, xls.file.name.offshore,
#                           start.time, max.shift = 4)%>% 
#   extract.all.vars()

data.inshore <- get.data(Year = Year, 
                         xls.file.name = xls.file.name.inshore, 
                         sheet.name = sheet.name.inshore,
                         col.types = col.types.inshore, 
                         col.names = col.names.inshore, 
                         start.time = start.time,
                         max.shift = 4)  %>%
  mutate(Area = "in")
  
data.offshore <- get.data(Year = Year,
                          xls.file.name = xls.file.name.offshore,
                          sheet.name = sheet.name.offshore,
                          col.types = col.types.offshore,
                          col.names = all_of(col.names.offshore),
                          start.time = start.time, 
                          max.shift = 4)

data.offshore %>% 
  filter(Mother_Calf > 0) %>%
  rbind(data.inshore) %>%
  arrange(Date.date, Minutes_since_0000) %>% 
  extract.all.vars() -> data.all


out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")

out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = 7, 
                          end.hr = 19, 
                          max.shift = 4)%>% extract.shift.vars()

formatted.all.data <- format.output(data.shift, max.shift = 4)

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all)

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift)

if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")
```




## 2006

```{r}
Year <- 2006
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[1])
xls.file.name.offshore <- paste0(data.dir, dir.name, "/", xls.files[2])

sheet.name.inshore <- "LOGS"
sheet.name.offshore <- "LOGS"

col.names.inshore <- c("DATE",	"EVENT", 	"TIME",	"OBS#",
                       "VIS IN",	"SEA ST",	"C/C")

col.types.inshore <- c("date", "numeric", "text", "numeric", 
                       "numeric", "text", "numeric", "numeric", 
                       "text", "text", "text", "text", 
                       "text", "text", "text")

col.names.offshore <- c("DATE",	"EVENT",	"TIME",	"OBS",	
                        "VIS",	"SEA ST",	"C/C")

col.types.offshore <- c("date", "numeric", "text", "numeric", 
                        "numeric", "text", "numeric", "numeric", 
                        "text", "text",  "text", "text")

# 
# data.all <- get.all.data(sheet.name.inshore, sheet.name.offshore,
#                           col.types.inshore, col.types.offshore,
#                           col.names.inshore, col.names.offshore,
#                           Year, xls.file.name.inshore, xls.file.name.offshore,
#                           start.time, max.shift = 4)%>% 
#   extract.all.vars()

data.inshore <- get.data(Year = Year, 
                         xls.file.name = xls.file.name.inshore, 
                         sheet.name = sheet.name.inshore,
                         col.types = col.types.inshore, 
                         col.names = col.names.inshore, 
                         start.time = start.time,
                         max.shift = 4) %>%
  mutate(Area = "in")
  

data.offshore <- get.data(Year = Year,
                          xls.file.name = xls.file.name.offshore,
                          sheet.name = sheet.name.offshore,
                          col.types = col.types.offshore,
                          col.names = all_of(col.names.offshore),
                          start.time = start.time, 
                          max.shift = 4)

data.offshore %>% 
  filter(Mother_Calf > 0) %>%
  rbind(data.inshore) %>%
  arrange(Date.date, Minutes_since_0000) %>% 
  extract.all.vars() -> data.all


out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")

out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = 7, 
                          end.hr = 19, 
                          max.shift = 4)%>% extract.shift.vars()

# same as before. Vis and SeaState are probably not filled in. 

formatted.all.data <- format.output(data.shift, max.shift = 4)

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all)

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift)

if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")

```



## 2007

```{r}
Year <- 2007
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[1])
xls.file.name.offshore <- paste0(data.dir, dir.name, "/", xls.files[2])

sheet.name.inshore <- "log"
sheet.name.offshore <- "log"

col.names.inshore <- c("DATE",	"EVENT", 	"TIME",	"OBS#",
                       "VIS IN",	"SEA ST",	"C/C")

col.types.inshore <- c("date", "numeric", "text", "numeric", 
                       "numeric", "text", "numeric", "numeric", 
                       "text", "text", "text", "text", 
                       "text", "text", "text", "text")

# data.out <- read_excel(xls.file.name.inshore,
#                          sheet = sheet.name.inshore,
#                          col_types = col.types.inshore)

# data.inshore <- get.data(Year = Year,
#                          dir.name = dir.name,
#                          xls.file.name = xls.file.name.inshore,
#                          sheet.name = sheet.name.inshore,
#                          col.types = col.types.inshore,
#                          col.names = col.names.inshore,
#                          area.name = "inshore",
#                          start.time = start.time)


col.names.offshore <- c("DATE",	"EVENT",	"TIME",	"OBS",	
                        "VIS",	"SEA ST",	"C/C")

col.types.offshore <- c("date", "numeric", "text", "numeric", 
                        "numeric", "text", "numeric", "numeric", 
                        "text", "text",  "text", "text")

# 
# data.all <- get.all.data(sheet.name.inshore, sheet.name.offshore,
#                           col.types.inshore, col.types.offshore,
#                           col.names.inshore, col.names.offshore,
#                           Year, xls.file.name.inshore, xls.file.name.offshore,
#                           start.time, max.shift = 4)%>% 
#   extract.all.vars()

data.inshore <- get.data(Year = Year, 
                         xls.file.name = xls.file.name.inshore, 
                         sheet.name = sheet.name.inshore,
                         col.types = col.types.inshore, 
                         col.names = col.names.inshore, 
                         start.time = start.time,
                         max.shift = 4) %>%
  mutate(Area = "in")
  

data.offshore <- get.data(Year = Year,
                          xls.file.name = xls.file.name.offshore,
                          sheet.name = sheet.name.offshore,
                          col.types = col.types.offshore,
                          col.names = all_of(col.names.offshore),
                          start.time = start.time, 
                          max.shift = 4)

data.offshore %>% 
  filter(Mother_Calf > 0) %>%
  rbind(data.inshore) %>%
  arrange(Date.date, Minutes_since_0000) %>% 
  extract.all.vars() -> data.all


out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")

out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = 7, 
                          end.hr = 19, 
                          max.shift = 4)%>% extract.shift.vars()

# same as before. Vis and SeaState are probably not filled in. 

formatted.all.data <- format.output(data.shift, max.shift = 4)

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all)

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift)

if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")

```




## 2008

```{r}
Year <- 2008
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[1])
xls.file.name.offshore <- paste0(data.dir, dir.name, "/", xls.files[2])

sheet.name.inshore <- "LOG"
sheet.name.offshore <- "LOGS"

col.names.inshore <- c("DATE",	"EVENT", 	"TIME",	"OBS#",
                       "VIS IN",	"SEA ST",	"C/C")

col.types.inshore <- c("date", "numeric", "text", "numeric", 
                       "numeric", "text", "numeric", "numeric", 
                       "text", "text", "text", "text", 
                       "text", "text", "text")

col.names.offshore <- c("DATE",	"EVENT",	"TIME",	"OBS",	
                        "VIS",	"SEA ST",	"C/C")

col.types.offshore <- c("date", "numeric", "text", "numeric", 
                        "numeric", "text", "numeric", "numeric", 
                        "text", "text",  "text", "text")

# 
# data.all <- get.all.data(sheet.name.inshore, sheet.name.offshore,
#                           col.types.inshore, col.types.offshore,
#                           col.names.inshore, col.names.offshore,
#                           Year, xls.file.name.inshore, xls.file.name.offshore,
#                           start.time, max.shift = 4)%>% 
#   extract.all.vars()

data.inshore <- get.data(Year = Year, 
                         xls.file.name = xls.file.name.inshore, 
                         sheet.name = sheet.name.inshore,
                         col.types = col.types.inshore, 
                         col.names = col.names.inshore, 
                         start.time = start.time,
                         max.shift = 4) %>%
  mutate(Area = "in")
  
data.offshore <- get.data(Year = Year,
                          xls.file.name = xls.file.name.offshore,
                          sheet.name = sheet.name.offshore,
                          col.types = col.types.offshore,
                          col.names = all_of(col.names.offshore),
                          start.time = start.time, 
                          max.shift = 4)

data.offshore %>% 
  filter(Mother_Calf > 0) %>%
  rbind(data.inshore) %>%
  arrange(Date.date, Minutes_since_0000) %>% 
  extract.all.vars() -> data.all


out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")

out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = 7, 
                          end.hr = 19, 
                          max.shift = 4)%>% extract.shift.vars()

# same as before. Vis and SeaState are probably not filled in. 

formatted.all.data <- format.output(data.shift, max.shift = 4)

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all)

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift)

if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")

```


## 2009

```{r}
Year <- 2009
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[1])
xls.file.name.offshore <- paste0(data.dir, dir.name, "/", xls.files[2])

sheet.name.inshore <- "LOGS"
sheet.name.offshore <- "LOGS"

col.names.inshore <- c("DATE",	"EVENT", 	"TIME",	"OBS#",
                       "VIS IN",	"SEA ST",	"C/C")

col.types.inshore <- c("date", "numeric", "text", "numeric", 
                       "numeric", "text", "numeric", "numeric", 
                       "text", "text", "text", "text", 
                       "text", "text", "text")


col.names.offshore <- c("DATE",	"EVENT",	"TIME",	"OBS",	
                        "VIS",	"SEA ST",	"C/C")

col.types.offshore <- c("date", "numeric", "text", "numeric", 
                        "numeric", "text", "numeric", "numeric", 
                        "text", "text",  "text", "text")

# 
# data.all <- get.all.data(sheet.name.inshore, sheet.name.offshore,
#                           col.types.inshore, col.types.offshore,
#                           col.names.inshore, col.names.offshore,
#                           Year, xls.file.name.inshore, xls.file.name.offshore,
#                           start.time, max.shift = 4)%>% 
#   extract.all.vars()

data.inshore <- get.data(Year = Year, 
                         xls.file.name = xls.file.name.inshore, 
                         sheet.name = sheet.name.inshore,
                         col.types = col.types.inshore, 
                         col.names = col.names.inshore, 
                         start.time = start.time,
                         max.shift = 4) %>%
  mutate(Area = "in")
  

data.offshore <- get.data(Year = Year,
                          xls.file.name = xls.file.name.offshore,
                          sheet.name = sheet.name.offshore,
                          col.types = col.types.offshore,
                          col.names = all_of(col.names.offshore),
                          start.time = start.time, 
                          max.shift = 4)

data.offshore %>% 
  filter(Mother_Calf > 0) %>%
  rbind(data.inshore) %>%
  arrange(Date.date, Minutes_since_0000) %>% 
  extract.all.vars() -> data.all



out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")

out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = 7, 
                          end.hr = 19, 
                          max.shift = 4)%>% extract.shift.vars()

formatted.all.data <- format.output(data.shift, max.shift = 4)

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all)

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift)

if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")

```


Files seem to be about the same from these years... 



## 2010

```{r}
Year <- 2010
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[2])
xls.file.name.offshore <- paste0(data.dir, dir.name, "/", xls.files[3])

sheet.name.inshore <- "LOGS"
sheet.name.offshore <- "LOGS"

col.names.inshore <- c("DATE",	"EVENT", 	"TIME",	"OBS#",
                       "VIS IN",	"SEA ST",	"C/C")

col.types.inshore <- c("date", "numeric", "text", "numeric", 
                       "numeric", "text", "numeric", "numeric", 
                       "text", "text", "text", "text", 
                       "text", "text", "text")


col.names.offshore <- c("DATE",	"EVENT",	"TIME",	"OBS",	
                        "VIS",	"SEA ST",	"C/C")

col.types.offshore <- c("date", "numeric", "text", "numeric", 
                        "numeric", "text", "numeric", "numeric", 
                        "text", "text",  "text", "text")

# 
# data.all <- get.all.data(sheet.name.inshore, sheet.name.offshore,
#                           col.types.inshore, col.types.offshore,
#                           col.names.inshore, col.names.offshore,
#                           Year, xls.file.name.inshore, xls.file.name.offshore,
#                           start.time, max.shift = 4)%>% 
#   extract.all.vars()

data.inshore <- get.data(Year = Year, 
                         xls.file.name = xls.file.name.inshore, 
                         sheet.name = sheet.name.inshore,
                         col.types = col.types.inshore, 
                         col.names = col.names.inshore, 
                         start.time = start.time,
                         max.shift = 4) %>%
  mutate(Area = "in")
  
data.offshore <- get.data(Year = Year,
                          xls.file.name = xls.file.name.offshore,
                          sheet.name = sheet.name.offshore,
                          col.types = col.types.offshore,
                          col.names = all_of(col.names.offshore),
                          start.time = start.time, 
                          max.shift = 4)

data.offshore %>% 
  filter(Mother_Calf > 0) %>%
  rbind(data.inshore) %>%
  arrange(Date.date, Minutes_since_0000) %>% 
  extract.all.vars() -> data.all



out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")

out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = 7, 
                          end.hr = 19, 
                          max.shift = 4)%>% extract.shift.vars()

# same as before. Vis and SeaState are probably not filled in. 

formatted.all.data <- format.output(data.shift, max.shift = 4)

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all)

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift)

if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")
```



## 2011

```{r}
Year <- 2011
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[2])
xls.file.name.offshore <- paste0(data.dir, dir.name, "/", xls.files[3])

sheet.name.inshore <- "LOGS"
sheet.name.offshore <- "LOGS"

col.names.inshore <- c("DATE",	"EVENT", 	"TIME",	"OBS#",
                       "VIS IN",	"SEA ST",	"C/C")

col.types.inshore <- c("date", "numeric", "text", "numeric", 
                       "numeric", "text", "numeric", "numeric", 
                       "text", "text", "text", "text", 
                       "text", "text", "text")


col.names.offshore <- c("DATE",	"EVENT",	"TIME",	"OBS",	
                        "VIS",	"SEA ST",	"C/C")

col.types.offshore <- c("date", "numeric", "text", "numeric", 
                        "numeric", "text", "numeric", "numeric", 
                        "text", "text",  "text", "text")

# 
# data.all <- get.all.data(sheet.name.inshore, sheet.name.offshore,
#                           col.types.inshore, col.types.offshore,
#                           col.names.inshore, col.names.offshore,
#                           Year, xls.file.name.inshore, xls.file.name.offshore,
#                           start.time, max.shift = 4)%>% 
#   extract.all.vars()

data.inshore <- get.data(Year = Year, 
                         xls.file.name = xls.file.name.inshore, 
                         sheet.name = sheet.name.inshore,
                         col.types = col.types.inshore, 
                         col.names = col.names.inshore, 
                         start.time = start.time,
                         max.shift = 4) %>%
  mutate(Area = "in")
  
data.offshore <- get.data(Year = Year,
                          xls.file.name = xls.file.name.offshore,
                          sheet.name = sheet.name.offshore,
                          col.types = col.types.offshore,
                          col.names = all_of(col.names.offshore),
                          start.time = start.time, 
                          max.shift = 4)

data.offshore %>% 
  filter(Mother_Calf > 0) %>%
  rbind(data.inshore) %>%
  arrange(Date.date, Minutes_since_0000) %>% 
  extract.all.vars() -> data.all



out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")

out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = 7, 
                          end.hr = 19, 
                          max.shift = 4)%>% extract.shift.vars()

# same as before. Vis and SeaState are probably not filled in. 

formatted.all.data <- format.output(data.shift, max.shift = 4)

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all)

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift)

if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")

```



## 2012

```{r}
Year <- 2012
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[2])
xls.file.name.offshore <- paste0(data.dir, dir.name, "/", xls.files[3])

sheet.name.inshore <- "LOGS"
sheet.name.offshore <- "LOGS"

col.names.inshore <- c("DATE",	"EVENT", 	"TIME",	"OBS#",
                       "VIS IN",	"SEA ST",	"C/C")

col.types.inshore <- c("date", "numeric", "text", "numeric", 
                       "numeric", "text", "numeric", "numeric", 
                       "text", "text", "text", "text", 
                       "text", "text", "text")


col.names.offshore <- c("DATE",	"EVENT",	"TIME",	"OBS",	
                        "VIS",	"SEA ST",	"C/C")

col.types.offshore <- c("date", "numeric", "text", "numeric", 
                        "numeric", "text", "numeric", "numeric", 
                        "text", "text",  "text", "text")

# 
# data.all <- get.all.data(sheet.name.inshore, sheet.name.offshore,
#                           col.types.inshore, col.types.offshore,
#                           col.names.inshore, col.names.offshore,
#                           Year, xls.file.name.inshore, xls.file.name.offshore,
#                           start.time, max.shift = 4)%>% 
#   extract.all.vars()

data.inshore <- get.data(Year = Year, 
                         xls.file.name = xls.file.name.inshore, 
                         sheet.name = sheet.name.inshore,
                         col.types = col.types.inshore, 
                         col.names = col.names.inshore, 
                         start.time = start.time,
                         max.shift = 4) %>%
  mutate(Area = "in")
  

data.offshore <- get.data(Year = Year,
                          xls.file.name = xls.file.name.offshore,
                          sheet.name = sheet.name.offshore,
                          col.types = col.types.offshore,
                          col.names = all_of(col.names.offshore),
                          start.time = start.time, 
                          max.shift = 4)

data.offshore %>% 
  filter(Mother_Calf > 0) %>%
  rbind(data.inshore) %>%
  arrange(Date.date, Minutes_since_0000) %>% 
  extract.all.vars() -> data.all


out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")

out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = 7, 
                          end.hr = 19, 
                          max.shift = 4)%>% extract.shift.vars()

# same as before. Vis and SeaState are probably not filled in. 

formatted.all.data <- format.output(data.shift, max.shift = 4)

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all)

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift)

if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")

```



## 2013

```{r}
Year <- 2013
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[1])
xls.file.name.offshore <- paste0(data.dir, dir.name, "/", xls.files[2])

sheet.name.inshore <- "LOGS"
sheet.name.offshore <- "LOGS"

col.names.inshore <- c("DATE",	"EVENT", 	"TIME",	"OBS#",
                       "VIS IN",	"SEA ST",	"C/C")

col.types.inshore <- c("date", "numeric", "text", "numeric", 
                       "numeric", "text", "numeric", "numeric", 
                       "text", "text", "text", "text", 
                       "text", "text", "text")


col.names.offshore <- c("DATE",	"EVENT",	"TIME",	"OBS",	
                        "VIS",	"SEA ST",	"C/C")

col.types.offshore <- c("date", "numeric", "text", "numeric", 
                        "numeric", "text", "numeric", "numeric", 
                        "text", "text",  "text", "text")

# 
# data.all <- get.all.data(sheet.name.inshore, sheet.name.offshore,
#                           col.types.inshore, col.types.offshore,
#                           col.names.inshore, col.names.offshore,
#                           Year, xls.file.name.inshore, xls.file.name.offshore,
#                           start.time, max.shift = 4)%>% 
#   extract.all.vars()

data.inshore <- get.data(Year = Year, 
                         xls.file.name = xls.file.name.inshore, 
                         sheet.name = sheet.name.inshore,
                         col.types = col.types.inshore, 
                         col.names = col.names.inshore, 
                         start.time = start.time,
                         max.shift = 4) %>%
  mutate(Area = "in")
  

data.offshore <- get.data(Year = Year,
                          xls.file.name = xls.file.name.offshore,
                          sheet.name = sheet.name.offshore,
                          col.types = col.types.offshore,
                          col.names = all_of(col.names.offshore),
                          start.time = start.time, 
                          max.shift = 4)

data.offshore %>% 
  filter(Mother_Calf > 0) %>%
  rbind(data.inshore) %>%
  arrange(Date.date, Minutes_since_0000) %>% 
  extract.all.vars() -> data.all



out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")

out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = 7, 
                          end.hr = 19, 
                          max.shift = 4)%>% extract.shift.vars()

# same as before. Vis and SeaState are probably not filled in. 

formatted.all.data <- format.output(data.shift, max.shift = 4)

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all)

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift)

if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")
```



## 2014

```{r}
Year <- 2014
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")

xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[grep("INSHORE", xls.files)])
xls.file.name.offshore <- paste0(data.dir, dir.name, "/", xls.files[grep("OFFSHORE", xls.files)])

sheet.name.inshore <- "LOGS"
sheet.name.offshore <- "LOGS"

col.names.inshore <- c("DATE",	"EVENT", 	"TIME",	"OBS#",
                       "VIS IN",	"SEA ST",	"C/C", "IN/OFF")

col.types.inshore <- c("date", "numeric", "text", "numeric", 
                       "numeric", "text", "numeric", "numeric", 
                       "text", "text", "text", "text", 
                       "text", "text", "text")

col.names.offshore <- c("DATE",	"EVENT",	"TIME",	"OBS",	
                        "VIS",	"SEA ST",	"C/C")

col.types.offshore <- c("date", "numeric", "text", "numeric", 
                        "numeric", "text", "numeric", "numeric", 
                        "text", "text",  "text", "text")

start.hr <- 7
end.hr <- 19
max.shift <- 4

data.inshore <- get.data(Year = Year,
                         xls.file.name = xls.file.name.inshore,
                         sheet.name = sheet.name.inshore, 
                         col.types = col.types.inshore,
                         col.names = all_of(col.names.inshore),
                         start.time = start.time,
                         max.shift = max.shift) %>%
  mutate(Area = "in")
  
data.offshore <- get.data(Year = Year,
                          xls.file.name = xls.file.name.offshore,
                          sheet.name = sheet.name.offshore,
                          col.types = col.types.offshore,
                          col.names = all_of(col.names.offshore),
                          start.time = start.time, 
                          max.shift = 4)

data.offshore %>% 
  filter(Mother_Calf > 0) %>%
  rbind(data.inshore) %>%
  arrange(Date.date, Minutes_since_0000) %>% 
  extract.all.vars() -> data.all

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = start.hr, 
                          end.hr = end.hr, 
                          max.shift = max.shift)%>% extract.shift.vars()

formatted.all.data <- format.output(data.shift, max.shift = max.shift)

out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")
out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all,
            quote = "none")

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift, 
            quote = "none")

# Need to remove NA to be used in Collating and Formatting v2.R
if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")


```


## 2015

```{r}
Year <- 2015
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")

xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[grep("INSHORE", xls.files)])
xls.file.name.offshore <- paste0(data.dir, dir.name, "/", xls.files[grep("OFFSHORE", xls.files)])

sheet.name.inshore <- "LOGS"
sheet.name.offshore <- "LOGS"

col.names.inshore <- c("DATE",	"EVENT", 	"TIME",	"OBS#",
                       "VIS IN",	"SEA ST",	"C/C", "IN/OFF")

col.types.inshore <- c("date", "numeric", "text", "numeric", 
                       "numeric", "text", "numeric", "numeric", 
                       "text", "text", "text", "text", 
                       "text", "text", "text")

col.names.offshore <- c("DATE",	"EVENT",	"TIME",	"OBS",	
                        "VIS",	"SEA ST",	"C/C")

col.types.offshore <- c("date", "numeric", "text", "numeric", 
                        "numeric", "text", "numeric", "numeric", 
                        "text", "text",  "text", "text")
start.hr <- 7
end.hr <- 19
max.shift <- 4

data.inshore <- get.data(Year = Year,
                         xls.file.name = xls.file.name.inshore,
                         sheet.name = sheet.name.inshore, 
                         col.types = col.types.inshore,
                         col.names = all_of(col.names.inshore),
                         start.time = start.time,
                         max.shift = max.shift)

data.offshore <- get.data(Year = Year,
                          xls.file.name = xls.file.name.offshore,
                          sheet.name = sheet.name.offshore,
                          col.types = col.types.offshore,
                          col.names = all_of(col.names.offshore),
                          start.time = start.time, 
                          max.shift = 4)

data.offshore %>% 
  filter(Mother_Calf > 0) %>%
  rbind(data.inshore) %>%
  arrange(Date.date, Minutes_since_0000) %>% 
  extract.all.vars() -> data.all

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = start.hr, 
                          end.hr = end.hr, 
                          max.shift = max.shift)%>% extract.shift.vars()

formatted.all.data <- format.output(data.shift, max.shift = max.shift)

out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")
out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all,
            quote = "none")

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift, 
            quote = "none")

# Need to remove NA to be used in Collating and Formatting v2.R
if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")


```



## 2016

```{r}
Year <- 2016
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[grep("INSHORE", xls.files)])
xls.file.name.offshore <- paste0(data.dir, dir.name, "/", xls.files[grep("OFFSHORE", xls.files)])

sheet.name.inshore <- "LOGS"
sheet.name.offshore <- NULL

col.names.inshore <- c("DATE",	"EVENT", 	"TIME",	"OBS#",
                       "VIS IN",	"SEA ST",	"C/C", "IN/OFF")

col.types.inshore <- c("date", "numeric", "text", "numeric", 
                       "numeric", "text", "numeric", "numeric", 
                       "text", "text", "text", "text", 
                       "text", "text", "text")

col.names.offshore <- c("DATE",	"EVENT",	"TIME",	"OBS",	
                        "VIS",	"SEA ST",	"C/C")

col.types.offshore <- c("date", "numeric", "text", "numeric", 
                        "numeric", "text", "numeric", "numeric", 
                        "text", "text",  "text", "text")

start.hr <- 7
end.hr <- 19
max.shift <- 4

data.inshore <- get.data(Year = Year,
                         xls.file.name = xls.file.name.inshore,
                         sheet.name = sheet.name.inshore, 
                         col.types = col.types.inshore,
                         col.names = all_of(col.names.inshore),
                         start.time = start.time,
                         max.shift = max.shift)

data.offshore <- get.data(Year = Year,
                          xls.file.name = xls.file.name.offshore,
                          sheet.name = sheet.name.offshore,
                          col.types = col.types.offshore,
                          col.names = all_of(col.names.offshore),
                          start.time = start.time, 
                          max.shift = 4)

# Effort can be different between inshore and offshore, so they have to be 
# computed separately...
# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R

data.offshore %>% 
  filter(Mother_Calf > 0) %>%
  rbind(data.inshore) %>%
  arrange(Date.date, Minutes_since_0000) %>% 
  extract.all.vars()-> data.all

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = start.hr, 
                          end.hr = end.hr, 
                          max.shift = max.shift) %>% extract.shift.vars()

formatted.all.data <- format.output(data.shift, max.shift = max.shift)

# data.shift.inshore <- find.effort(data.inshore, 
#                                   start.hr = start.hr, 
#                                   end.hr = end.hr, 
#                                   max.shift = max.shift)
# 
# formatted.inshore.data <- format.output(data.shift.inshore, max.shift = max.shift)
# 
# data.shift.offshore <- find.effort(data.offshore, 
#                                   start.hr = start.hr, 
#                                   end.hr = end.hr, 
#                                   max.shift = max.shift)
# 
# formatted.offshore.data <- format.output(data.shift.offshore, max.shift = max.shift)
# 
# data.offshore %>% 
#   filter(Mother_Calf > 0) %>%
#   rbind(data.inshore) %>%
#   arrange(Date.date, Minutes_since_0000) -> data.all


out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")
out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all,
            quote = "none")

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift, 
            quote = "none")

# Need to remove NA to be used in Collating and Formatting v2.R
if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")
```


## 2017

No offshore log exists for 2017
```{r}
Year <- 2017
dir.name <- paste0("C_C ", Year)
start.time <- "0700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[1])

sheet.name <- "LOGS"

col.names <- c("DATE",	"EVENT", 	"TIME",	"OBS#",
               "VIS IN",	"SEA ST",	"C/C", "IN/OFF")

col.types <- c("date", "numeric", "text", "text", 
               "numeric", "text", "numeric", "numeric", 
               "text", "text", "text", "text", 
               "text", "text", "text", "text",
               "text", "text")

start.hr <- 7
end.hr <- 19
max.shift <- 4

# get the data using get.data function, which is in Piedras_Blancas_fcns.R
data.all <- get.data(Year = Year,
                     xls.file.name = xls.file.name.inshore,
                     sheet.name = sheet.name,
                     col.types = col.types,
                     col.names = all_of(col.names),
                     start.time = start.time,
                     max.shift = 4)%>% 
  extract.all.vars()

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = start.hr, 
                          end.hr = end.hr, 
                          max.shift = max.shift) %>% extract.shift.vars()

formatted.all.data <- format.output(data.shift, max.shift = max.shift)

out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")
out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all,
            quote = "none")

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift, 
            quote = "none")

# Need to remove NA to be used in Collating and Formatting v2.R
if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")


```



## 2018

No offshore log exists for 2018
```{r}
Year <- 2018
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[1])

sheet.name <- "LOGS"

col.names <- c("DATE",	"EVENT", 	"TIME",	"OBS#",
               "VIS IN",	"SEA ST",	"C/C", "IN/OFF")

col.types <- c("numeric", "date", "numeric", "text", "text", 
                       "numeric", "text", "numeric", "numeric", 
                       "text", "text", "text", "text", 
                       "text", "text", "text", "text",
                       "text", "text", "text", "text")

start.hr <- 7
end.hr <- 19
max.shift <- 4

# get the data using get.data function, which is in Piedras_Blancas_fcns.R
data.all <- get.data(Year = Year,
                     xls.file.name = xls.file.name.inshore,
                     sheet.name = sheet.name,
                     col.types = col.types,
                     col.names = all_of(col.names),
                     start.time = start.time,
                     max.shift = 4)%>% 
  extract.all.vars()

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = start.hr, 
                          end.hr = end.hr, 
                          max.shift = max.shift) %>% extract.shift.vars()

formatted.all.data <- format.output(data.shift, max.shift = max.shift)


out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")
out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all,
            quote = "none")

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift, 
            quote = "none")

# Need to remove NA to be used in Collating and Formatting v2.R
if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")


```





## 2019

No offshore log exists for 2019
```{r}
Year <- 2019
dir.name <- paste0("C_C ", Year)
start.time <- "700"

xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[1])

# Event for 4/29/2019 at 1845 was changed from "1" to "4". 2022-06-24
# Event for 5/9/2019 at 0830 was changed from "1" to "3". 2022-06-24
# Event for 5/23/2019 at 1200 was changed from "1" to "3". 2022-06-24

sheet.name <- "INSHORE LOGS"

col.names <- c("DATE",	"EVENT", 	"TIME",	"OBS #",
               "VIS IN",	"SEA ST",	"C/C", "IN/OFF")

col.types <- c("date", "numeric", "numeric", "text", "text", 
                       "numeric", "text", "numeric", "numeric", 
                       "text", "text", "text", "text", 
                       "text", "text", "text", "text",
                       "text", "text", "text")

start.hr <- 7
end.hr <- 19
max.shift <- 4

# get the data using get.data function, which is in Piedras_Blancas_fcns.R
data.all <- get.data(Year = Year,
                     xls.file.name = xls.file.name.inshore,
                     sheet.name = sheet.name,
                     col.types = col.types,
                     col.names = all_of(col.names),
                     start.time = start.time,
                     max.shift = 4)%>% 
  extract.all.vars()

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = start.hr, 
                          end.hr = end.hr, 
                          max.shift = max.shift) %>% extract.shift.vars()

formatted.all.data <- format.output(data.shift, max.shift = max.shift)


out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")
out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all,
            quote = "none")

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift, 
            quote = "none")

# Need to remove NA to be used in Collating and Formatting v2.R
if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")


```


No data for 2020 - COVID.

## 2021

```{r}
Year <- 2021
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[1])

# Event for 4/20/2021 at 745 was changed from "3" to "5". 2022-06-24
sheet.name <- "INSHORE LOGS"

col.names <- c("DATE",	"EVENT", 	"TIME",	"OBS #",
                       "VIS IN",	"SEA ST",	"C/C", "IN/OFF")

col.types <- c("date", "numeric", "numeric", "text", "text", 
                       "numeric", "text", "numeric", "numeric", 
                       "text", "text", "text", "text", 
                       "text", "text", "text", "text",
                       "text", "text", "text", "text", "text")

# get the data using get.data function, which is in Piedras_Blancas_fcns.R
data.all <- get.data(Year = Year,
                     xls.file.name = xls.file.name.inshore,
                     sheet.name = sheet.name,
                     col.types = col.types,
                     col.names = all_of(col.names),
                     start.time = start.time,
                     max.shift = 4)%>% 
  extract.all.vars()

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = 7, 
                          end.hr = 19, 
                          max.shift = 4) %>% extract.shift.vars()

formatted.all.data <- format.output(data.shift, max.shift = 4)

out.file.name.all <- paste0(out.dir, "Processed_all_data_", 
                            Year, ".csv")
out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

if (!file.exists(out.file.name.all))
  write_csv(data.all,
            file = out.file.name.all,
            quote = "none")

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift, 
            quote = "none")

# Need to remove NA to be used in Collating and Formatting v2.R
if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")

```


## 2022

For 2022 and beyond, I added some code here to skip using Collating and Formatting v2.R. It's much easier to get all necessary steps done here, directly out of Excel input files than going through many scripts. 

```{r}
# PROBLEM WITH AT LEAST ONE SHIFT 2022-03-28 ENDING/STARTING AT NOT EXACTLY AT THE 
# TOP OF THE HOUR (1558 INSTEAD OF 1600). THIS SHOULD BE EDITED IN THE DATA FILE. 
# CONTINUE HERE 2022-06-22  -> IT HAS BEEN EDITED TO 1600 2022-06-23

Year <- 2022
dir.name <- paste0("C_C ", Year)
start.time <- "700"
xls.files <- list.files(path = paste0(data.dir, dir.name), pattern = ".xls")
xls.file.name.inshore <- paste0(data.dir, dir.name, "/", xls.files[1])

sheet.name <- "MomCalf Logs 2022 postQC"
# c("Date", "Event", "Time", "Obs. Code", 
#  "Sea State", "Vis. IN", "Cow  / Calf")

# These are not the names of all columns. These are the names of columns in the
# spreadsheet that are needed. These names change among years, so they need to
# be specified for each year.
col.names <- c("DATE", 	"EVENT", 	"TIME",	"OBS #",
               "SEA ST", "VIS IN", "M/C", "LOCATION (IN/OFF)")

# these are column types of all columns in the spreadsheet. 
col.types <- c("date", "numeric", "numeric", "text", "text", 
               "numeric", "numeric", "numeric", "numeric", "text", 
               "text", "text", "text", "numeric", "text", 
               "text", "text", "text")

# get the data using get.data function, which is in Piedras_Blancas_fcns.R
data.all <- get.data(Year = Year,
                     xls.file.name = xls.file.name.inshore,
                     sheet.name = sheet.name,
                     col.types = col.types,
                     col.names = all_of(col.names),
                     start.time = start.time,
                     max.shift = 4)%>% 
  extract.all.vars()

# calculate effort and other statistics per 3-hr shift, using find.effort
# function in Piedras_Blancas_fcns.R
data.shift <- find.effort(data.all, 
                          start.hr = 7, 
                          end.hr = 19, 
                          max.shift = 4) %>% extract.shift.vars() 

formatted.all.data <- format.output(data.shift, max.shift = 4)

out.file.name.all <- paste0(out.dir, "Processed_all_data_",
                            Year, ".csv")
out.file.name.shift <- paste0(out.dir, "Processed_by_shift_data_", 
                              Year, ".csv")

out.file.name.formatted <- paste0(out.formatted.dir,
                                  Year, " Formatted.csv")

if (!file.exists(out.file.name.all))
  write_csv(data.all ,
            file = out.file.name.all,
            quote = "none")

if (!file.exists(out.file.name.shift))
  write_csv(data.shift,
            file = out.file.name.shift, 
            quote = "none")

# Need to remove NA to be used in Collating and Formatting v2.R
if (!file.exists(out.file.name.formatted))
  write_csv(formatted.all.data,
            file = out.file.name.formatted, 
            quote = "none",
            na = "")

```

